---
title: "Replication: 'The Distributive Politics of Enforcement'"
author: "Beau Meche"
date: "2/21/2020"
output: pdf_document
bibliography: "bibliography1.bib"
#biblio-style: "chicagolike"
link_citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# toolbox

# gt from github: 'remotes::install_github("rstudio/gt")'


library(tidyverse)
library(foreign)
library(stargazer)
library(tinytex)
library(gt)
library(bibtex)
```

#### Title:
The Distributive Politics of Enforcement


#### Author:
Alisha C. Holland


#### Overview: 
This paper looks at police behavior in varying contexts around Latin America to explore what gets prosecuted and what is allowed to go unnoticed. The areas of interest are the relationships between constituency of the powers that be (at a given time) and how much those individuals in the constituent groups care to have property rights enforced. Involving (what I believe is) original research, the author does an intriguing job of addressing this question in a rather Bayesian way, so I thought this would be a good project on a topic that I briefly studied previously and can now apply new skills to.  


#### <u>A Quote from the Abstract:</u>

"Why do some politicians tolerate the violation of the law? In contexts where the poor are the primary violators of property laws, I argue that the answer lies in the electoral costs of enforcement: Enforcement can decrease support from poor voters even while it generates support among nonpoor voters. Using an original data set on unlicensed street vending and enforcement operations at the subcity district level in three Latin American capital cities, I show that the combination of voter demographics and electoral rules explains enforcement. Supported by qualitative interviews, these findings suggest how the intentional nonenforcement of law, or forbearance, can be an electoral strategy. Dominant theories based on state capacity poorly explain the results." 

-Alisha C. Holland
[@Holland14]

```{r load_and_triage_data, echo = FALSE}
# this was the link code before I did the bibliography: 
# <a href="https://github.com/BeauMeche/enforcement_distribution_electorate">link</a>

# this project was done in STATA, so transcribing the code will likely be rough
# as my knowledge of STATA is negligible


# may as well take everything out of the zip file

unzip("Holland_dataverse_repl_01.zip")

enforcement <- read.dta("Enforcement.dta")

```

My code repository is linked at the end of the document if you're interested.^[[Check Out My Repo Here!](https://github.com/BeauMeche/enforcement_distribution_electorate)]

\newpage
#### Initial Data Exploration
```{r data_exploration, echo=FALSE}

# variable "lower" is the share of lower-class residents in a given district

glimpse(enforcement)


enforcement %>% 
  filter(city == "lima") %>%
  ggplot(aes(x = corruption, y = operations)) +
  geom_point(aes(color = poor)) +
  labs(
    title = "Corruption Coefficients and Police Activity",
    x = "Number of Operations",
    y = "Corruption Scale",
    color = "% Poor
Population"
  ) +
  scale_x_continuous(breaks = (seq(0,20, by= 2)))

# currently can't seem to use lm()... unsure why...

```






\newpage
#### An Interesting Chart of Average Arrest Rates per District in Santiago, Chile

I am unsure what's going on with Santiago, Santiago, but that is a question for later. 
```{r mstone_4_gtTable, echo=FALSE}

gt1 <- enforcement %>% 
  filter(city == "santiago") %>% 
  select(arrests, city, district, population) %>% 
  # mutate(marrest = mean(arrests),
  #        mcorrupt = mean(corruption),
  #        mtax = mean(tax)) %>% 
  mutate(arrpercap = round(arrests/population, 3)) %>% 
  group_by(district) %>% 
  drop_na() %>% 
  summarise(avg_arrestPC = mean(arrpercap))

gt1 %>% 
  # mutate(avg_arrests = round(`mean(arrests)`, 2)) %>%
  # select(!`mean(arrests)`) %>%
  arrange(desc(avg_arrestPC)) %>%
  gt() %>% 
  fmt_percent(columns = vars(avg_arrestPC)) %>% 
  cols_label(avg_arrestPC = "Arrest Rate",
             district = "District") %>% 
  tab_header(
    title = "Average Per Capita Arrest Rate per District",
    subtitle = "Districts from the city of Santiago"
    ) 


```




\newpage
#### References: 


